---
title: "Report"
author: "Your Name Here"
format: pdf
editor: source
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
#load("output/met_area.RData")
library(ggplot2)
library(texreg)
```

# Introduction

A paragraph to introduce the research question

# Data and Methods

A couple of paragraphs to describe where the different data come from and how they were processed and to describe the method of analysis.

Here is a template code chunk for producing a figure. Be sure to change the name of the code chunk if you copy and paste it.

# Analysis

Show how the key independent and dependent variables are distributed. Use graphical techniques to show the bivariate relationship of interest and then show multivariate model results and interpret them.

```{r}
#| label: fig-template
#| fig-cap: A Caption

# Code for the figure below. You should change the label from "fig-template" to something relevant but it should start with "fig-". You can then reference this figure in the tex with @fig-whatever-you-called-it

# Each figure should go in a separate code chunk.
# replace this code with a real figure
ggplot(mtcars, aes(x=cyl, y=mpg))+
  geom_point()+
  theme_bw()
```

```{r}
#| label: tbl-reg
#| tbl-cap: A Caption
#| results: asis

# build your models here - change these
model1 <- lm(mpg~cyl+disp, data=mtcars)
model2 <- lm(mpg~cyl+disp+hp, data=mtcars)
model3 <- lm(mpg~cyl+disp+hp+wt, data=mtcars)

#to print to screen replace texreg with screenreg
texreg(list(model1, model2, model3),
        #custom.coef.names = c("Covariate labels here"), #uncomment to add nice labels to independent variables
        digits = 3,
        caption.above=TRUE, 
        include.rsquared=TRUE,
        include.adjrs=FALSE,
        include.nobs=TRUE,
        include.rmse=FALSE)
```

# Conclusions

A paragraph to summarize the findings.
